\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}      
\usepackage[english]{babel} %utilisation du package français
%
%
%
\usepackage{textcomp}% améliore certains symboles de bases
\usepackage{lmodern}% remplace la police ComputerModern par LatinModern (+ mieux bien)
%
%
%
\usepackage{mathtools}% compléments à amsmath
\usepackage{amssymb,amsfonts}% symboles mathématiques supplémentaires
\usepackage{amsthm}% environnement ams-theorem
\usepackage[colorlinks,breaklinks,bookmarks,plainpages=false,unicode=true]{hyperref}%
\usepackage{todonotes} %ajouter des commentaires
%\usepackage[disable]{todonotes}%cache les commentaires
\usepackage{datetime} %ajoute la date et l'heure
%
%
\newcounter{mycomment}
\newcommand{\mycomment}[2][]{\refstepcounter{mycomment}{\todo[color={green!33},size=\small]{\textbf{[\uppercase{#1}\themycomment]:}~#2}}}
\newcommand{\PH}[1]{\todo[color={blue!33},size=small]{\textbf{PH :} #1}}
\newcommand{\PHInline}[1]{\todo[color={blue!33},size=small,inline]{\textbf{PH :} #1}}
\newcommand{\GS}[1]{\mycomment[GS]{#1}}
%
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{external,graphs}
\tikzexternalize[prefix=Images/]% On externalise. Les images sont stockées dans le dossier Images
\makeatletter %pour ne pas prendre en compte les todo dans l'externalisation
\renewcommand{\todo}[2][]{\tikzexternaldisable\@todo[#1]{#2}\tikzexternalenable}
\makeatother
\makeatletter %pour ne pas prendre en compte les missingfigures dans l'externalisation
\renewcommand{\missingfigure}[2][]{\tikzexternaldisable\@missingfigure[#1]{#2}\tikzexternalenable}
\makeatother
\tikzset{myloop above/.style={loop, out=130, in = 50,min distance =8mm}}
\tikzset{myloop below/.style={loop, out=-130, in = -50,min distance =8mm}}
\tikzset{blacknode/.style={shape= circle, fill = black, inner sep = 0pt, outer sep = 0pt, minimum size = 3pt,draw}}
%
\newtheorem{lem}{Lemma}[section]
\newtheorem{conjecture}[lem]{Conjecture}
\newtheorem{cor}[lem]{Corollary}
\newtheorem{prop}[lem]{Proposition}
\newtheorem{thm}[lem]{Theorem}
\theoremstyle{definition}
\newtheorem{defn}[lem]{Definition}
\theoremstyle{remark}% texte en roman
\newtheorem{exmp}[lem]{Example}
%
%
%
\DeclareMathOperator\Cayley{Cayl}
\DeclareMathOperator\Sch{Sch}
\DeclareMathOperator\stab{Stab}
\DeclareMathOperator\ab{ab}
%
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\newcommand*{\field}[1]{\mathbf{#1}}
\newcommand*{\Z}{\field{Z}}
\newcommand{\setst}[2]{\{#1\ |\ #2\}}
%
%
\title{Property FW and wreath products of groups: a~simple approach using Schreier graphs}
\author{Paul-Henry Leemann\thanks{Supported by grant 200021\textunderscore188578 of the Swiss National Fund for Scientific Research.}, Grégoire Schneeberger}
\date{\today \quad \currenttime}
%
%
%
%
%
%
%
%
%
%
\begin{document}
\maketitle
%
%
%
%
%
%
%
%
%
%
\begin{abstract}
The group property FW stands in-between the celebrated Kazdhan's property (T) and Serre's property FA. Among many characterizations, it might be defined, for finitely generated groups, as having all Schreier graphs one-ended.
%Yves Cornulier proved that a finitely generated wreath product $G\wr_XH$ has property FW if and only if both $G$ and $H$ have property FW and $X$ is finite. In this paper, we will present a more explicit combinatorial elementary proof using Schreier graphs. \GS{Ajouté que c'est déjà dans Cornulier}

It follows from the work of Y. Cornulier that a finitely generated wreath product $G\wr_XH$ has property FW if and only if both $G$ and $H$ have property FW and $X$ is finite.
%In this paper, we will present a more explicit combinatorial elementary proof using Schreier graphs.
The aim of this paper is to give an elementary, direct and explicit proof of this fact using Schreier graphs.\PH{Légèrement reformulé.}
\end{abstract}
%
%
%
%
%
%
%
%
%
%
%
%
%
%
%
\input{Introduction_v3.tex}
\input{Definitions_v3.tex}
\input{Proof_v3.tex}
%
%
%
%
%
%
%
%
%
%
\begin{thebibliography}{10}

\bibitem{Barnhill2008}
Angela Barnhill and Indira Chatterji.
\newblock Property ({T}) versus property {FW}.
\newblock {\em Enseign. Math. (2)}, 54(1-2):16--18, 2008.

\bibitem{MR1213151}
Stephen~G Brick.
\newblock {Quasi-isometries and ends of groups}.
\newblock {\em J. Pure Appl. Algebr.}, 86(1):23--33, 1993.

\bibitem{Cherix2004}
Pierre-Alain Cherix, Florian Martin, and Alain Valette.
\newblock Spaces with measured walls, the {H}aagerup property and property
  ({T}).
\newblock {\em Ergodic Theory Dynam. Systems}, 24(6):1895--1908, 2004.

\bibitem{Cornulier2013}
Yves {Cornulier}.
\newblock {Group actions with commensurated subsets, wallings and cubings}.
\newblock {\em arXiv e-prints}, page arXiv:1302.5982, February 2013.

\bibitem{Cornulier2011}
Yves Cornulier and Aditi Kar.
\newblock On property ({FA}) for wreath products.
\newblock {\em J. Group Theory}, 14(1):165--174, 2011.

\bibitem{DelaHarpe2000}
Pierre de~la Harpe.
\newblock {\em Topics in geometric group theory}.
\newblock Chicago Lectures in Mathematics. University of Chicago Press,
  Chicago, IL, 2000.

\bibitem{MR1967888}
Reinhard Diestel and Daniela K\"{u}hn.
\newblock Graph-theoretical versus topological ends of graphs.
\newblock {\em J. Combin. Theory Ser. B}, 87(1):197--206, 2003.

\bibitem{MR0450121}
Jonathan~L. Gross.
\newblock Every connected regular graph of even degree is a {S}chreier coset
  graph.
\newblock {\em J. Combinatorial Theory Ser. B}, 22(3):227--232, 1977.

\bibitem{MR10267}
Heinz Hopf.
\newblock Enden offener {R}\"{a}ume und unendliche diskontinuierliche
  {G}ruppen.
\newblock {\em Comment. Math. Helv.}, 16:81--100, 1944.

\bibitem{LS2021}
Paul-Henry Leemann and Gr{\'e}goire Schneeberger.
\newblock Wreath products of groups acting with bounded orbits.
\newblock {\em arXiv e-prints}, page arXiv:2102.08001, February 2021.

\bibitem{MR1358635}
Alexander Lubotzky.
\newblock Cayley graphs: eigenvalues, expanders and random walks.
\newblock In {\em Surveys in combinatorics, 1995 ({S}tirling)}, volume 218 of
  {\em London Math. Soc. Lecture Note Ser.}, pages 155--189. Cambridge Univ.
  Press, Cambridge, 1995.

\bibitem{Neuhauser2005a}
Markus Neuhauser.
\newblock Relative property ({T}) and related properties of wreath products.
\newblock {\em Math. Z.}, 251(1):167--177, 2005.

\bibitem{MR1347406}
Michah Sageev.
\newblock Ends of group pairs and non-positively curved cube complexes.
\newblock {\em Proc. London Math. Soc. (3)}, 71(3):585--617, 1995.

\end{thebibliography}

%
%
%
%
%
\enddocument